%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
% Resume in Latex
% Author : Shubham Mazumder
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}


%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}

% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}


% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}


% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }



% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\begin{flushleft}
	\textbf{\large Muhammad Abbas} \\
	\textit{Karachi, Pakistan} $|$
	\textit{+92-308-5685919} $|$
	% \href{https://website}{{\textit{@website}}} $|$
	\href{mailto:abbastaqvi81@gmail.com}{{\textit{@mail}}} $|$
	\href{https://linkedin.com/in/abbastaqvi}{{\textit{@linkedin}}} $|$
	\href{https://github.com/smabbasht}{{\textit{@github}}}
	\vspace{-8pt}
\end{flushleft}

% -------------------------------------
%---------- PROFESSIONAL SUMMARY ------
% -------------------------------------

\section{Professional Summary}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
	{\item{
            {Focused \highlight{Data Engineer} with a \highlight{Bachelor's in
            Computer Science} from \highlight{Habib University}, Distinguished
            for experience in \highlight{Rust} and \highlight{Data Science} on
            top of experience with \highlight{Data Engineering tools}, with a
            track record of collaboratively and independently delivering
            \highlight{convertible PoCs} and then developing
            \highlight{production tools} that saves several runtime hours of
            cloud machines for fintech industry. Well versed in architectural
            planning for Big data. Delivering well-documented, tested, and
            operable code. Efficient in collaborating and communicating new
            ideas and opinions and evaluating the existing ones}
          \\ 
    }}
\end{itemize}
\sectionspace

% -------------------------------------
%----------TECHNICAL SKILLS------------
% -------------------------------------

\section{Technical Skills}
\subheadingtitlevspace
\begin{itemize}[leftmargin=0.15in, label={}]
	{\item{
          \titleItem{Languages}{: Rust, Python, Scala, C/C++, Golang, SQL (Postgres, MSSQL,
          MySQL), NoSQL (MongoDB), HTML, CSS, JS (basic)} \\
          \titleItem{Data Eng. Tools}{: Spark, NiFi, Airflow, Databricks, Informatica}\\
          \titleItem{Software Frameworks}{: Axum, Actix, Django, Flutter, RestFramework}\\
          \titleItem{AI Frameworks}{: Tensorflow, PyTorch, JAX, NumPyro}\\
          \titleItem{Cloud, DevOps and API Tools}{: AWS, Azure Cloud, GCP, Git,
          Docker, Kubernetes, Postman, Linux (Longtime Desktop User)} \\
          \titleItem{Others}{: Polars, Pandas, Design Patterns, Debugging, Root
          Cause Analysis, Architecture Planning, Working with JSON \& Parquet}
	}}
\end{itemize}
\sectionspace




% -------------------------------------
%----------EXPERIENCE------------------
% -------------------------------------

\section{Experience}
\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Data Engineer I}} $|$ \emph{Logiciel Services LLC.} $-$ \small{United States}}{\small{Full-time} $|$ May 2024 --------- Present}
\resumeItemListStart
\resumeItem{Developed Rust pipelines for EOD processing of FIX logs to CAT
files, C\# pipeline previously running in 500mins, got optimized to 50mins with
Rust \& Nifi, saving around 400 mins daily on AWS machine.} 
\resumeItem{Orchestrated the data ingestion, transformation and AI pipelines
through airflow DAGs, triggering pipelines of Nifi, Spark, Rust and AI (Python)
on daily basis.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Data Engineer I}} $|$ \emph{ImproData} $-$ \small{Victoria, Austrailia}}{ \small{Part-time} $|$ Dec 2023 -- March 2024 }
\resumeItemListStart
\resumeItem{Worked on Azure Databricks (PySpark) for risk management of
cyber-security data, building bronze, silver and gold layers.}
\resumeItem{Worked on automated pipeline dev using GCP Cloud Functions to
transfer compressed json bulk data from local to GCS \& population to BigQuery}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{DevOps Intern}} $|$ \emph{Pullflow Inc.} $-$ \small{San Jose, California}}{\small{Full-time} $|$ July 2023 - Aug 2023}
\resumeItemListStart
\resumeItem{Worked on AWS EKS (Kubernetes) and Docker as I was responsible for
designing \& implementing the infrastructure that was on AWS to on-premise
server.}
\resumeItem{Worked on Budibase Dashboarding \& hosting it on
pullflow subdomain using traefik for loadbalancing.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Data Engineering Intern}} $|$ \emph{United Bank Limited} $-$ \small{Karachi, Pakistan}}{\small{Full-time} $|$ May 2023 -- Jun 2023}
\resumeItemListStart
\resumeItem{Built a pipeline using Informatica for streaming ingestion
of UBL’s data from Qatar \& Bahrain in Hive Data Lake.}
\resumeItem{Participated in architecture analysis of data ingestion to datalake
of data from UBL Qatar \& Bahrain to ensure that the production AI pipelines
running in realtime on UBL Pak's data can be used for data from Qatar \&
Bahrain.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Data Analyst Intern}} $|$ \emph{Edlab Pakistan} $-$ \small{Karachi, Pakistan}}{\small{Part-time} $|$ Sep 2021 -- Oct 2021}
\resumeItemListStart
\resumeItem{Worked on Data Collection, Cleaning, Manipulation and Organization
using NumPy, Pandas and Excel for Demographic Educational Data}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Student Mentor}} $|$ \emph{Habib University} $-$ \small{Karachi, Pakistan}}{\small{Part-time} $|$ Aug 2023 -- May 2024}
\resumeItemListStart
\resumeItem{\underline{Teaching Assistant for Data Structures \& Algorithms:}
Assisted students during labs and with assignments.}
\resumeItem{\underline{Git \& Github Workshop Instructor:} Conducted
two workshops on Git and GitHub.}
\resumeItem{\underline{Teaching Assistant for Data Structures \& Algorithms:}
Assisted students during labs and with assignments DSA.}
\resumeItemListEnd
\resumeSubHeadingListEnd
% -------------------------------------
%----------EDUCATION-------------------
% -------------------------------------

% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {University of Utah}{Salt Lake City, UT}
%       {MS in Computer Science | GPA: 3.86}{January 2021 -- December 2023} 
%     \resumeSubheading
%       {SRM University}{Chennai, TN, India}
%       {Bachelor of Technology in Computer Science and Engineering | GPA: 3.4}{August 2012 -- May 2016}
%   \resumeSubHeadingListEnd
% \vspace{-12pt}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Habib University}{GPA : 3.31}
{BS in Computer Science}{August 2020 -- June 2024}
\resumeSubHeadingListEnd
\vspace{-8pt}

% -------------------------------------
%----------PROJECTS--------------------
% -------------------------------------

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{Astroflow} $|$ \emph{PyTorch, Numpyro, Django, Postgres, SQLite, Javascript}}{Nov 2023}
\resumeItemListStart
\resumeItem{A Deep Learning framework of Normalizing flows for estimating population parameters of Binary Black holes under the leadership of RIT instructor.}
\resumeItem{Ut consequat semper viverra nam libero justo laoreet sit amet. Feugiat nisl pretium fusce id velit ut tortor pretium.}
\resumeItemListEnd
\resumeProjectHeading
{\titleItem{Lox Interpreter} $|$ \emph{Python, numpy. D3.js}}{Spring 2022}
\resumeItemListStart
\resumeItem{Ut consequat semper viverra nam libero justo laoreet sit amet. Feugiat nisl pretium fusce id velit ut tortor pretium.}
\resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor. }
\resumeItemListEnd
\resumeProjectHeading
{\titleItem{Ferroflow} $|$ \emph{\LaTeX}}{November 2021}
\resumeItemListStart
\resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor. }
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

About

About us
Our values
Careers
Press & awards
Blog

Learn
